Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-25 paper/paper.tex
Finished first draft of problem section

For this experimetn, we use Amazon's book data. Books are rated by users on a 1
to 5 star-scale. As in 
Some stuff about the experiment details: the data we use, how we subtract the
biases, the biasedness of the experimental dataset, training vs testing.

>>>>

For this experiment, we use Amazon's book data. Books are rated by users on a 1
to 5 star-scale. Before any analysis of the data, we remove the biases from each
rating, as in \cite{Koren2009}:
\begin{align}
\hat{r_{ui}} = r_{ui} - \mu_r - b_i - b_u
\end{align}
where $r_{ui}$ is the raw rating user $u$ gave item $i$, $\mu_r$ is the average
rating over the entire dataset, $b_i$ is the item bias, calculated as the
average rating for item $i$ after $\mu_r$ has been subtracted from each, and 
$b_u$ is the user bias, calculated as the average rating from user $u$ after
$\mu_r$ and $b_i$ have been subtracted from each.
